### 2013-12-09 abstract.tex
updated volume Rsq and errors to Matlab vars

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on their stiffness.  In this study, MR and ARFI imaging
datasets were compared to one another and with gross pathology measurements
made immediately post radical prostatectomy.  Images were manually segmented to
delineate the central gland (CG) and prostate capsule, and 3D models were
rendered to evaluate zonal anatomy dimensions and volumes.  Both imaging
modalities showed moderate correlations between estimated organ volume and
gross pathologic weights.  ARFI and MR total prostate gland volumes were
well-correlated (R$^2$ = 0.63), but ARFI images yielded prostate volumes that
were, on average, larger (6.1\% $\pm$ 25\%) than MR images, primarily due to
over-estimation of the lateral dimension of the total gland
(\ARFImrTotalLatLatMeanPct $\pm$ \ARFImrTotalLatLatStdPct\%), while
over-estimates of the other dimensions were less significant
(\ARFImrTotalAntPostMeanPct $\pm$ \ARFImrTotalAntPostStdPct\% and
\ARFImrTotalApexBaseMeanPct $\pm$ \ARFImrTotalApexBaseStdPct\%).  The ARFI and
MR CG volumes were also moderately correlated (R$^2$ = 0.38).  CG volume
differences were attributed to under-estimation of the apex-to-base axis
(\ARFImrCentralApexBaseMeanPct $\pm$ \ARFImrCentralApexBaseStdPct\%), and
over-estimation bias in the lateral dimension (\ARFImrCentralLatLatMeanPct
$\pm$ \ARFImrCentralLatLatStdPct\%).  ARFI prostate imaging yielded prostate
volumes and dimensions that were correlated with MR T2WI estimates, with biases
in the AP dimension, most likely related to poor displacement SNR in the
anterior region of the prostate from greater distance from the rectal wall
imaging surface.  Lateral dimension contrast was also challenging due to
peri-prostatic fat.  ARFI imaging is a promising low-cost, real-time imaging
modality that can compliment MR imaging for diagnosis, treatment planning and
management of PCa.

>>>>

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on their stiffness.  In this study, MR and ARFI imaging
datasets were compared to one another and with gross pathology measurements
made immediately post radical prostatectomy.  Images were manually segmented to
delineate the central gland (CG) and prostate capsule, and 3D models were
rendered to evaluate zonal anatomy dimensions and volumes.  Both imaging
modalities showed moderate correlations between estimated organ volume and
gross pathologic weights.  ARFI and MR total prostate gland volumes were
well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded prostate volumes that
were, on average, larger (\MRarfiVolTotalMeanDiff\% $\pm$ \MRarfiVolTotalStdDiff\%) than MR images, primarily due to
over-estimation of the lateral dimension of the total gland
(\ARFImrTotalLatLatMeanPct $\pm$ \ARFImrTotalLatLatStdPct\%), while
over-estimates of the other dimensions were less significant
(\ARFImrTotalAntPostMeanPct $\pm$ \ARFImrTotalAntPostStdPct\% and
\ARFImrTotalApexBaseMeanPct $\pm$ \ARFImrTotalApexBaseStdPct\%).  The ARFI and
MR CG volumes were also well-correlated (R$^2$ = \MRarfiVolCentralRsq).  CG volume
differences were attributed to under-estimation of the apex-to-base axis
(\ARFImrCentralApexBaseMeanPct $\pm$ \ARFImrCentralApexBaseStdPct\%), and
over-estimation bias in the lateral dimension (\ARFImrCentralLatLatMeanPct
$\pm$ \ARFImrCentralLatLatStdPct\%).  ARFI prostate imaging yielded prostate
volumes and dimensions that were correlated with MR T2WI estimates, with biases
in the AP dimension, most likely related to poor displacement SNR in the
anterior region of the prostate from greater distance from the rectal wall
imaging surface.  Lateral dimension contrast was also challenging due to
peri-prostatic fat.  ARFI imaging is a promising low-cost, real-time imaging
modality that can compliment MR imaging for diagnosis, treatment planning and
management of PCa.

### 2013-12-09 conclusions.tex
updated volume Rsq and errors to Matlab vars

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = 0.63), but ARFI images yielded prostate volumes
that were, on average, larger (6.1\% $\pm$ 25\%) than MR images, primarily due
to over-estimation of the lateral dimension of the prostate total gland (13.5
$\pm$ 11.0\%), while over-estimates of the other dimensions were less
significant contributors (5.7 $\pm$ 20.6\% and 2.4 $\pm$ 17.0\%).  The central
zone volumes of ARFI and MR images were also moderately correlated (R$^2$ =
0.38), with minimal volume bias between the imaging modalities, but significant
variability case-to-case (-5.0 $\pm$ 39.5\%).  Central zone volume differences
were, again, strongly attributed to over-estimation of the lateral dimension
(11.5 $\pm$ 22.5\%), with a significant underestimation of the
anterior-to-posterior dimension (-6.1 $\pm$ 21.1\%).  Strong variability in
central gland volumes is believed to be related to the extent of benign
prostatic hyperplasia (BPH) for select cases.  Overall, ARFI imaging of the
prostate yielded prostate volumes and dimensions that were correlated with MR
T2WI estimates, with biases in the anterior-to-posterior dimension, most likely
related to poor displacement SNR in the anterior region of the prostate from
greater distance from the rectal wall imaging surface, and the lateral
dimension, where contrast between the PZ and peri-prostatic fat could be
limited.  ARFI imaging is a promising low-cost, real-time imaging modality that
can compliment MR imaging for diagnosis, treatment planning and management of
PCa.

>>>>

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded
prostate volumes that were, on average, larger (\MRarfiVolTotalMeanDiff\%~$\pm$
\MRarfiVolTotalStdDiff\%) than MR images, primarily due to over-estimation of
the lateral dimension of the prostate total gland (\ARFImrTotalLatLatMeanPct~
$\pm$ \ARFImrTotalLatLatStdPct\%), while over-estimates of the other dimensions
were less significant contributors (\ARFImrTotalAntPostMeanPct~$\pm$
\ARFImrTotalAntPostStdPct\%~and \ARFImrTotalApexBaseMeanPct~$\pm$
\ARFImrTotalApexBaseStdPct\%).  The central zone volumes of ARFI and MR images
were also well-correlated (R$^2$ = \MRarfiVolCentralRsq), with minimal volume
bias between the imaging modalities, but significant variability case-to-case
(\MRarfiVolCentralMeanDiff~$\pm$ MRarfiVolCentralStdDiff\%).  Central zone
volume differences were, again, strongly attributed to over-estimation of the
lateral dimension (\ARFImrCentralLatLatMeanPct~$\pm$
\ARFImrCentralLatLatStdPct\%), with a significant underestimation of the
anterior-to-posterior dimension (\ARFImrCentralAntPostMeanPct~$\pm$
\ARFImrCentralAntPostStdPct\%).  Strong variability in central gland volumes is
believed to be related to the extent of benign prostatic hyperplasia (BPH) for
select cases.  Overall, ARFI imaging of the prostate yielded prostate volumes
and dimensions that were correlated with MR T2WI estimates, with biases in the
anterior-to-posterior dimension, most likely related to poor displacement SNR
in the anterior region of the prostate from greater distance from the rectal
wall imaging surface, and the lateral dimension, where contrast between the PZ
and peri-prostatic fat could be limited.  ARFI imaging is a promising low-cost,
real-time imaging modality that can compliment MR imaging for diagnosis,
treatment planning and management of PCa.

### 2013-12-09 results.tex
updated volume Rsq and errors to Matlab vars

\section{Results}\label{sect:results}
The subvolumes associated with the zonal anatomy in each imaging modality were
measured (Figure~\ref{fig:mr_arfi_volumes}(a)), with moderate correlation
between the ARFI and MR total prostate gland volumes (R$^2$ = 0.63), with a
mean overestimation of of 6.1 $\pm$ 25.0\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:mr_arfi_volumes}(b)).  Central gland volumes were
slightly less correlated between ARFI and MR images (R$^2$ = 0.38) with no
significant mean over/under-estimation (-5.0 $\pm$ 39.5\%), but significant
variability between the cases (Figure~\ref{fig:mr_arfi_volumes}(c)).
Table~\ref{tab:mr_arfi_volumes} has the individually-measured volumes for MR
and ARFI imaging for each study subject.

>>>>

\section{Results}\label{sect:results}
The subvolumes associated with the zonal anatomy in each imaging modality were
measured (Figure~\ref{fig:mr_arfi_volumes}(a)), with moderate correlation
between the ARFI and MR total prostate gland volumes (R$^2$ =
\MRarfiVolTotalRsq), with a mean overestimation of of
\MRarfiVolTotalMeanDiff~$\pm$ \MRarfiVolTotalStdDiff\% by ARFI imaging compared
to MR volumes (Figure~\ref{fig:mr_arfi_volumes}(b)).  Central gland volumes
were well-correlated between ARFI and MR images (R$^2$ = \MRarfiVolCentralRsq)
with no significant mean over/under-estimation (\MRarfiVolCentralMeanDiff~$\pm$
\MRarfiVolCentralStdDiff\%), but significant variability between the cases
(Figure~\ref{fig:mr_arfi_volumes}(c)).  Table~\ref{tab:mr_arfi_volumes} has the
individually-measured volumes for MR and ARFI imaging for each study subject.
